### 2016-12-04 README.Rmd
minor tweaks

In this example, we fit a random forest to the Boston housing data. (See `?boston` for a brief explanation of the data.) Note, for any of the following examples, you can see a progress bar by simply specifying `.progress = "text"` in the call to `partial`. You may also reduce the computation time via the `grid.resolution` option in the call to `partial`.
```{r, message = FALSE, warning=FALSE}
# Load required packages
library(ggmap)  # for plotting data on maps
library(pdp)  # for constructing PDPs
library(randomForest)  # for random forest algorithm

@@

# Using randomForest's partialPlot function
partialPlot(boston.rf, pred.data = boston, x.var = "lstat")

# Package pdp's partial function returns a data frame by default
head(partial(boston.rf, pred.var = "lstat"))  # returns a data frame

# Set `plot = TRUE` to return a "trellis" object
partial(boston.rf, pred.var = "lstat", plot = TRUE, rug = TRUE)

# The partial function allows for multiple predictors
partial(boston.rf, pred.var = c("lstat", "rm"), plot = TRUE, chull = TRUE)

# The plotPartial function offers more flexible plotting
pd <- partial(boston.rf, pred.var = c("lstat", "rm"))

# Default plot
plotPartial(pd)

# Customized plot
plotPartial(pd, levelplot = FALSE, zlab = "cmedv", drape = TRUE,
            colorkey = FALSE, screen = list(z = -20, x = -60))

# Look at partial dependence of median home value on location
pd.loc <- partial(boston.rf, pred.var = c("lon", "lat"), chull = TRUE)

# Overlay predictions on a map of Boston
# ll <- c(range(boston$lon), range(boston$lat))
# map <- get_map(location = ll[c(1, 3, 2, 4)], zoom = 11, maptype = "toner-lite")
# ggmap(map) + 
#   geom_point(aes(x = lon, y = lat), data = boston, alpha = 0.2) +
#   geom_tile(aes(x = lon, y = lat, z = y, fill = y), 
#             data = pd.loc, alpha = 0.3) +
#   geom_contour(color = "white", alpha = 0.5) +
#   scale_fill_distiller(palette = "Spectral", name = "Median\nvalue") +
#   coord_fixed(ratio = 1) +
#   labs(x = "Longitude", y = "Latitude")
```

@@

In this example, we fit a random forest to the Pima Indians diabetes data. (See `?pima` for a brief explanation of the data.)
```{r, message=FALSE, warning=FALSE}
# Fit a random forest to the Pima Indians diabetes data
data (pima)  # load the boston housing data
set.seed(102)  # for reproducibility
pima.rf <- randomForest(diabetes ~ ., data = pima, na.action = na.omit)

# Partial dependence of glucose on diabetes test result (neg/pos). This may take
# a couple minutes!
partial(pima.rf, pred.var = c("glucose", "age"), plot = TRUE, chull = TRUE)
```

@@

For illustration we use `caret`'s `train` function to tune a support vector machine (SVM) with a radial basis function kernel to the Pima Indians diabetes data using 5-fold cross-validation. We then use the final model to construct a PDPs for `glucose` and `age`. Note, when training a model using `caret`'s `train` function, you can view tuning progress by setting `verboseIter = TRUE` in the call to `trainControl`.
```{r, message=FALSE, warning=FALSE}
# Load required packages
library(caret)  # for model training/tuning

@@

# Tune a support vector machine (SVM) using a radial basis function kerel to
# the Pima Indians diabetes data
set.seed(103)  # for reproducibility
pima.svm <- train(diabetes ~ ., data = pima, method = "svmRadial",
                  prob.model = TRUE, na.action = na.omit, trControl = ctrl,
                  tuneLength = 10)

# Partial dependence of glucose on diabetes test result (neg/pos)
partial(pima.svm, pred.var = "glucose", plot = TRUE, rug = TRUE)

# Partial dependence of age on diabetes test result (neg/pos)
partial(pima.svm, pred.var = "age", plot = TRUE, rug = TRUE)

# Partial dependence of glucose and age on diabetes test result (neg/pos). This
# may take a couple minutes!
partial(pima.svm, pred.var = c("glucose", "age"), plot = TRUE, chull = TRUE)
```

>>>>

In this example, we fit a random forest to the Boston housing data. (See `?boston` for a brief explanation of the data.) Note, for any of the following examples, you can see a progress bar by simply specifying `.progress = "text"` in the call to `partial`. You may also reduce the computation time via the `grid.resolution` option in the call to `partial`.
```{r, message = FALSE, warning=FALSE, fig.show="hold"}
# Load required packages
library(pdp)  # for constructing PDPs
library(randomForest)  # for random forest algorithm

@@

# Partial dependence of lstat and rm on cmedv
partial(boston.rf, pred.var = "lstat", plot = TRUE, rug = TRUE)
partial(boston.rf, pred.var = "age", plot = TRUE, rug = TRUE)
partial(boston.rf, pred.var = c("lstat", "rm"), plot = TRUE, chull = TRUE)
```

@@

In this example, we fit a support vector machine with a radial basis function kernel to the Pima Indians diabetes data. (See `?pima` for a brief explanation of the data.)
```{r, message=FALSE, warning=FALSE, fig.show="hold"}
# Load required packages
library(kernlab)  # for fitting SVMs

# Fit an SVM to the Pima Indians diabetes data
data (pima)  # load the boston housing data
pima.svm <- ksvm(diabetes ~ ., data = pima, type = "C-svc", kernel = "rbfdot",
                 C = 0.5, prob.model = TRUE)

# Partial dependence of glucose and age on diabetes test result (neg/pos). 
partial(pima.svm, pred.var = c("glucose", "age"), plot = TRUE, chull = TRUE)
```

@@

For illustration we use `caret`'s `train` function to tune an [XGBoost](https://github.com/dmlc/xgboost) model to the Pima Indians diabetes data using 5-fold cross-validation. We then use the final model to construct PDPs for `glucose` and `age`. Note, when training a model using `caret`'s `train` function, you can view tuning progress by setting `verboseIter = TRUE` in the call to `trainControl`.
```{r, message=FALSE, warning=FALSE}
# Load required packages
library(caret)  # for model training/tuning

@@

# Grid of tuning parameter values
xgb.grid <- expand.grid(
  nrounds = 500,
  max_depth = 1:6,
  eta = c(0.001, 0.01, 0.1, 0.2, 0.3, 0.5),
  gamma = 0, 
  colsample_bytree = 1,
  min_child_weight = 1,
  subsample = 1
)

# Tune a support vector machine (SVM) using a radial basis function kerel to
# the Pima Indians diabetes data. This may take a few minutes!
set.seed(103)  # for reproducibility
pima.xgb <- train(diabetes ~ ., data = pima, method = "xgbTree",
                  prob.model = TRUE, na.action = na.omit, trControl = ctrl,
                  tuneGrid = xgb.grid)

# Partial dependence of glucose and age on diabetes test result (neg/pos)
partial(pima.xgb, pred.var = "glucose", plot = TRUE, rug = TRUE)
partial(pima.xgb, pred.var = "age", plot = TRUE, rug = TRUE)
partial(pima.xgb, pred.var = "mass", plot = TRUE, chull = TRUE)
```
